\mytitle

### 2021-12-08 paper.tex
adapt directory
extend text

@@

\cite{polylogarithm}

@@

@@

\lstinputlisting[language=C]{src/Li2.c}

>>>>

An algorithm for the computation of the real dilogarithm is presented,
which allows for the use of instruction\-/level parallelism.

@@

The dilogarithm \cite{lewin} is a special function, which appears in
many physics applications, for example in the calculation of quantum
corrections in quantum field theory.  The investigation of new models
beyond the Standard Model of particle physics with a large parameter
space require the evaluation of the dilogarithm (and other functions)
billions of times.  Such investigations thus require a fast evaluation
of the dilogarithm.  In the past many time-efficient algorithms have
been proposed \cite{}, which are implemented in program libraries for
numerical physics and mathematics \cite{root,gsl}.

The development of modern CPUs with support for instruction\-/level
parallelism (ILP) opens the opportunity for a further reduction of the
runtime of the calculation of the dilogarithm, given an appropriate
formulation of the algorithm.  In this paper an algorithm for the
calculation of the real dilogarithm $\Li$ is presented, which makes
use of ILP, resulting in a reduced runtime compared to the algorithms
presented so far.  A C implementation of this algorithm can be found
in the appendix and in the arXiv submission of this paper.

@@

C, C++ and FORTRAN implementations of the presented algorithm can be
found in the Polylogarithm package \cite{polylogarithm}.

@@

\lstinputlisting[language=C]{anc/Li2.c}
